---
title: "p8105_hw5_qra2000"
author: "Quinn Anderson"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

## Setup and load libraries

```{r setup, results=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(12345)
```

## Problem 2

Below is a tidy dataframe containing data from all participants, including the subject ID, control arm, and observations over time:

```{r}
load_study_data = list.files("./data", pattern = ".csv", all.files = FALSE, full.names = FALSE)

tidy_study_data = data.frame(participants = load_study_data) |> 
  mutate(
    file_contents = map(participants, ~read.csv(file.path("./data", .)))) |> 
  separate(participants, into = c("control", "subject_id")) |> 
  unnest(file_contents) |> 
  mutate(control = recode(control, `con` = "control", `exp` = "experiment")) |> 
  pivot_longer(week_1:week_8,
               names_to = "week", 
               values_to = "observation")

tidy_study_data
```

Below is a spaghetti plot showing observations on each subject over time.

```{r}
tidy_study_data |> 
  ggplot(aes(x = week, y = observation, group = subject_id, color = subject_id)) +
  geom_line() +
  labs(
    title = "Observations on Subject ID over Time",
       x = "Week",
       y = "Observation") +
  theme_minimal()
```

^^^

The spaghetti plot shows observations on each subject over time for the course of the longitudinal study. [put more description here]










